Untitled

### 2023-08-14 code/analysis_Redo.Rmd
last few updates

did2s(
      data = df.sum %>% inner_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite < 5),
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) ,
        cluster_var = "ID",
      verbose = FALSE
    )

>>>>

did2s(
      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% filter(is.na(DistToClosestSite) | DistToClosestSite > 5),
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) ,
        cluster_var = "ID",
      verbose = FALSE
    )

set.seed(345)
did2s(
      data = df.sum %>% left_join(df.z.dist %>% select(`Grant Number.y`, DistToClosestSite), by = c("Grant Number" = "Grant Number.y")) %>% 
        group_by(ID) %>% 
  mutate(DistToClosestSite = ifelse(is.na(DistToClosestSite), sample(size = 1, df.z.dist$DistToClosestSite, replace = T), DistToClosestSite)),
      yname = "NewQuality", 
      treatment = "Tx",
        first_stage = ~ 0 | ID + Year + Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.Children + MCD + MCR + COM, 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(DistToClosestSite / 1) + I(Tx *as.numeric(DistToClosestSite / 1)),
        cluster_var = "ID",
      verbose = FALSE
    )
